Hypertension and microbiome

### 2019-08-28 articletwo-sensitivityanalysis.Rmd
Smaller number of permutations

betadiversity.askbp <- calculate.betadiversity(pseq = pseq.species,
                                                matrix = bray.dist.m.species,
                                                vars = list("max" = var.CL.opt,
                                                            "min" = var.CL.min))

@@

betadiversity.healthy <- calculate.betadiversity(pseq = pseq.species.healthy,
                                                matrix = bray.dist.m.species.healthy,
                                                vars = list("max" = var.CL[var.CL != "PREVAL_DIAB"],
                                                            "min" = var.CL.min))

@@

>>>>

betadiversity.askbp <- calculate.betadiversity(pseq = pseq.species,
                                                matrix = bray.dist.m.species,
                                                vars = list("max" = var.CL.opt,
                                                            "min" = var.CL.min),
                                               npermutations = 999)

@@

betadiversity.healthy <- calculate.betadiversity(pseq = pseq.species.healthy,
                                                matrix = bray.dist.m.species.healthy,
                                                vars = list("max" = var.CL[var.CL != "PREVAL_DIAB"],
                                                            "min" = var.CL.min),
                                                npermutations = 999)

@@

## BMI

Normal weigth

```{r sensitivity analysis normal weight}
pseq.species.normalweight <- subset_samples(pseq.species, BMI > 18.5 & BMI <= 25)

bray.dist.m.species.normalweight <-
    bray.dist.m.species[pseq.species.normalweight %>% meta %>% rownames,
                        pseq.species.normalweight %>% meta %>% rownames]

alphadiversity.normalweight <- calculate.alphadiversity(pseq.species.normalweight,
                                                   list("max" = var.CL[var.CL != "BMI"],
                                                        "min" = var.CL.min))

betadiversity.normalweight <- calculate.betadiversity(pseq = pseq.species.normalweight,
                                                matrix = bray.dist.m.species.normalweight,
                                                vars = list("max" = var.CL[var.CL != "BMI"],
                                                            "min" = var.CL.min),
                                                npermutations = 999)

diversities.helthy <- mergediversities(alphadiversity.normalweight,
                                       betadiversity.normalweight,
                                       names.dset = names.dset)

plot.diversities(diversities.normalweight)
```

Obese

```{r sensitivity analysis obese}
pseq.species.obese <- subset_samples(pseq.species, BMI > 30 & BMI <= 40)

bray.dist.m.species.obese <-
    bray.dist.m.species[pseq.species.obese %>% meta %>% rownames,
                        pseq.species.obese %>% meta %>% rownames]

alphadiversity.obese <- calculate.alphadiversity(pseq.species.obese,
                                                   list("max" = var.CL[var.CL != "BMI"],
                                                        "min" = var.CL.min))

betadiversity.obese <- calculate.betadiversity(pseq = pseq.species.obese,
                                                matrix = bray.dist.m.species.obese,
                                                vars = list("max" = var.CL[var.CL != "BMI"],
                                                            "min" = var.CL.min),
                                               npermutations = 999)

diversities.helthy <- mergediversities(alphadiversity.obese,
                                       betadiversity.obese,
                                       names.dset = names.dset)

plot.diversities(diversities.obese)
```
